### 2022-11-07 lmcs/conclusion.tex
Fix typos & more uses of hfill

For the session-typed $\pi$-calculus, Dezani~\etal~\cite{dezani-ciancaglinimostrous06} guarantee progress by allowing only one active session at a time. Dezani~\cite{dezani-ciancagliniliguoro09progress} introduces a partial order on channels, similar to Kobayashi~\cite{kobayashi98}.
Carbone and Debois~\cite{carbonedebois10} define progress for session typed $\pi$-calculus in terms of a \emph{catalyser} which provides the missing counterpart to a process. Carbone~\etal~\cite{carbonedardha14} use catalysers to show that progress is a compositional form of lock-freedom and can be lifted to session types via the encoding of session types to linear types~\cite{kobayashi07,dardhagiachino12,dardha14beat}.
Vieira and Vasconcelos~\cite{vieiravasconcelos13} use single priorities and an abstract partial order to guarantee deadlock freedom in a binary session-typed $\pi$-calculus and building on conservation types.

>>>>

For the session-typed $\pi$-calculus, Dezani~\etal~\cite{dezani-ciancaglinimostrous06} guarantee progress by allowing only one active session at a time. Dezani~\cite{dezani-ciancagliniliguoro09progress} introduces a partial order on channels, similar to Kobayashi~\cite{kobayashi98}.
Carbone and Debois~\cite{carbonedebois10} define progress for session typed $\pi$-calculus in terms of a \emph{catalyser} which provides the missing counterpart to a process. Carbone~\etal~\cite{carbonedardha14} use catalysers to show that progress is a compositional form of lock-freedom and can be lifted to session types via the encoding of session types to linear types~\cite{kobayashi07,dardhagiachino12,dardha14beat}.
Vieira and Vasconcelos~\cite{vieiravasconcelos13} use single priorities and an abstract partial order to guarantee deadlock freedom in a binary session-typed $\pi$-calculus and building on conversation types.

### 2022-11-07 lmcs/introduction.tex
Fix typos & more uses of hfill

GV is a concurrent $\lambda$-calculus with \emph{binary} session types, where each channel is shared between exactly two processes. Binary session types guarantee two crucial properties \emph{communication safety}---\eg, if the protocol says to transmit an integer, you transmit an integer---and \emph{session fidelity}---\eg, if the protocol says send, you send. A third crucial property is \emph{deadlock freedom}, which ensures that processes do not have cyclic dependencies---\eg, when two processes wait for each other to send a value. Binary session types \emph{alone} are insufficient to rule out deadlocks arising from interleaved sessions, but several additional techniques have been developed to guarantee deadlock freedom in session-typed $\pi$-calculus and concurrent $\lambda$-calculus.

>>>>

GV is a concurrent $\lambda$-calculus with \emph{binary} session types, where each channel is shared between exactly two processes. Binary session types guarantee two crucial properties: \emph{communication safety}---\eg, if the protocol says to transmit an integer, you transmit an integer---and \emph{session fidelity}---\eg, if the protocol says send, you send. A third crucial property is \emph{deadlock freedom}, which ensures that processes do not have cyclic dependencies---\eg, when two processes wait for each other to send a value. Binary session types \emph{alone} are insufficient to rule out deadlocks arising from interleaved sessions, but several additional techniques have been developed to guarantee deadlock freedom in session-typed $\pi$-calculus and concurrent $\lambda$-calculus.
